\documentclass[12pt,courier]{navyletter}


\usepackage{designature}

\author{Dennis Evangelista}
\title{Letter of recommendation for Varun Bhagat}
\navysubj{Letter of recommendation for MIDN 2/c Varun Bhagat}
\navyfiling{}
\navyserial{}
\date{\today}
\navymarking{}

\begin{document}
\makedateblock{}

\begin{navyletterheader}
\navyfrom{Assistant Professor Dennis Jose Evangelista\newline Department of Weapons \& Systems Engineering}
\navyto{Lawrence Livermore National Laboratories\newline Summer Internships}
\navyskip%
%\navysubj{Letter of recommendation for MIDN 3/c Varun Bhagat}
\navysubjline%
%\navyskip{}%
%\navyref{refa}{CVN-71 letter Ser 1234, dtd 2 Jan 2016}
%\navyref{refb}{NAVSEA 250-1500-1 Nuclear Welding Manual}
%\navyref{refc}{Bettis letter Ser 5678, dtd 1 Feb 2016}
%\navyencl{encl1}{blah}
\end{navyletterheader}

\section{}
This letter of recommendation is on behalf of MIDN 2/c Varun Bhagat.  Mr.~Bhagat was a student in my Introduction to Systems Engineering course, taught to all systems engineering majors during their second year here at the Academy. The course focuses on getting students to think like engineers, as well as learn C (on an mbed microcontroller) and Matlab. Mr.~Bhagat excelled at all of these and received an A in the course. 

\section{} 
Among his highly competetive group of fellow engineering midshipmen, MIDN 2/c Bhagat distinguished himself with outstanding coding and presentation and communication skills.  He developed a highly entertaining shoe shining robot as well as a humorous video game in which a cartoon of the Commandant threw conduct offenses at a hapless midshipman, who then had to dodge them.  Every student here at the Academy is required to study some engineering, and the ones like Mr.~Bhagat, who thrive in engineering majors, are as intense as any MIT or Caltech power tool.  

\section{}
Over the term I have known him, I have been impressed by MIDN 2/c Bhagat's abilty to lead his peers.  Mr.~Bhagat has consistently taken charge to help all his group members meet deadlines and ensure a working project; he kept his groups on track and made sure they provided all required deliverables.  From personal experience, he is as skilled as any top second-year internship candidate from MIT, Harvard, or Berkeley.  I believe he would do well in an internship and will be of great benefit to Lawrence Livermore National Labs. 


\noclosing{}\\
\noindent\hspace*{4in}\includesignature{}
\signature{D EVANGELISTA}

%\copyto
%File
\end{document}